Generating Simulated Data

### 2021-03-17 docs/SimData.Rmd
add NOBA hydra sizebins

Species specific bin width definitions are an input into the model, with more refined (smaller) bin sizes during rapid growth phases.

Initially, we'll directly transfer bin widths for GB and NOBA common species:  
* Aherring = Norwegian_ssh,
* Acod = North_atl_cod, 
* haddock = Haddock, 
* Amackerel = Mackerel.

We will substitute bin widths from these GB species for NOBA:
* silverhake ~ Blue_whiting
* yellowtailfl ~ Long_rough_dab

NOBA Redfish
NOBA Saithe

NOBA Polar_cod and Capelin are smaller than any GB modeled species

NOBA Green_halibut are larger than any GB modeled species

These decisions will carry through to other life history parameters, at least initially.

@@

```{r fitpars}

>>>>

Species specific bin width definitions are an input into the model, with more refined (smaller) bin sizes during rapid growth phases. *Consider a function to do this using species max size and the desired number of bins for more consistency and to easily change Nsizebins.*

Initially, we'll directly transfer bin widths for GB and NOBA common species:

 *  Aherring = [Norwegian_ssh](https://www.hi.no/en/hi/temasider/species/herring) 
 *  Acod = [North_atl_cod](https://www.hi.no/en/hi/temasider/species/cod--northeast-arctic) (*but max size could be bigger in simulated data, may need to increase last bin*)
 *  haddock = [Haddock](https://www.hi.no/en/hi/temasider/species/haddock) (*but max size could be bigger in simulated data, may need to increase last bin*)
 *  Amackerel = [Mackerel](https://www.hi.no/en/hi/temasider/species/mackerel). (*note, should mackerel have smaller bin widths for fast early growth?*)

We will substitute bin widths from these similar taxa/size GB species for NOBA:

 *  silverhake ~ [Blue_whiting](https://www.hi.no/en/hi/temasider/species/blue-whiting)  
 *  yellowtailfl ~ [Long_rough_dab](https://www.sciencedirect.com/science/article/abs/pii/S1385110196907972) a.k.a. American plaice

We will modify or subsitute bin widths for the rest of the NOBA species based on size:

 *  NOBA [Redfish](https://www.hi.no/en/hi/temasider/species/redfish/beaked-redfish-in-the-barents-and-norwegian-seas) have a maximum size of 47 cm, use 5 x 10 cm bins  
 *  NOBA [Saithe](https://www.hi.no/en/hi/temasider/species/northeast-arctic-saithe) have a maximum size of 130 cm; use goosefish bins
 *  NOBA [Polar_cod](https://www.hi.no/en/hi/temasider/species/polar-cod) have a maximum size of 25 cm; use 5 x 5 cm bins  
 *  NOBA [Capelin](https://www.hi.no/en/hi/temasider/species/capelin-in-the-barents-sea) are smaller than any GB modeled species, max size 21 cm; use 5 x 5 cm bins  
 *  NOBA [Green_halibut](https://www.hi.no/en/hi/temasider/species/greenland-halibut) are large, max size 120 cm; use Acod bins

Code to make sizebins csv for input; hardcoded based on these decisions.

```{r sizebins, eval=FALSE}
# for reference, GB hydra_sim size bins
# sizeclass1,sizeclass2,sizeclass3,sizeclass4,sizeclass5,commentField-notused
# 20,20,20,20,30,spinydog
# 20,20,20,20,40,winterskate
# 5,5,5,5,20,Aherring
# 20,20,20,40,50,Acod
# 10,10,20,20,20,haddock
# 10,10,10,10,20,yellowtailfl
# 10,10,10,10,10,winterfl
# 10,10,10,10,10,Amackerel
# 10,10,10,10,30,silverhake
# 20,20,20,30,40,goosefish

sizebinmat <- matrix(0, singletons$Nspecies, singletons$Nsizebins, 
                dimnames = list(c(sort.default(sppsubset$Name)),  c(paste0("sizeclass",seq(1:singletons$Nsizebins)))))

sizebinmat["Blue_whiting",] <- c(10,10,10,10,30)
sizebinmat["Capelin",] <- c(5,5,5,5,5)
sizebinmat["Green_halibut",] <- c(20,20,20,40,50)
sizebinmat["Haddock",] <- c(10,10,20,20,20)
sizebinmat["Long_rough_dab",] <- c(10,10,10,10,20)
sizebinmat["Mackerel",] <- c(10,10,10,10,10)
sizebinmat["North_atl_cod",] <- c(20,20,20,40,50)
sizebinmat["Norwegian_ssh",] <- c(5,5,5,5,20)
sizebinmat["Polar_cod",] <- c(5,5,5,5,5)
sizebinmat["Redfish",] <- c(10,10,10,10,10)
sizebinmat["Saithe",] <- c(20,20,20,30,40)

sizebins <- as.data.frame(sizebinmat) %>%
  mutate('commentField-notused' = rownames(sizebinmat))

write_csv(sizebins, paste0(o.name,"length_sizebins_NOBA.csv"))

These decisions on matching species can carry through to other life history parameters, at least initially.

@@

```{r fitpars, eval=FALSE}
